%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

% This resume is the base resume which is heavy on data.

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage[default]{comfortaa}
\usepackage[T1]{fontenc}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Joel Varghese} \\ \vspace{1pt}
    \small +91 9136349025 $|$ \href{mailto:joel02varghese@gmail.com}{\underline{joel02varghese@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/joel02varghese/}{\underline{linkedin.com/in/joel02varghese/}} $|$
    \href{https://github.com/joel122002}{\underline{github.com/joel122002}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Mumbai}{Mumbai, India}
      {Bachelor of Engineering in Computer Engineering}{Aug. 2020 -- Jun. 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Development Engineer - I}{Apr. 2025 -- Present}
      {CarWale (CarTrade Tech)}{Mumbai, India}
      \resumeItemListStart
        \resumeItem{Worked on a microservices architecture leveraging .NET, C\#, React, RabbitMQ, MySQL, Memcached, and AWS to build scalable distributed systems serving 80M+ monthly users.}
        \resumeItem{Identified frequently used cacheable APIs and implemented CDN caching, easing load on the most utilized microservice, resulting in a 17\% drop in pod usage and ~45\% reduction in direct service calls.}
        \resumeItem{Proactively developed a page as a functional component with an optimized memoization strategy, achieving 50\% fewer re-renders than comparable pages.}
        \resumeItem{Analyzed client side errors and proposed a fix for 60\% of errors, improving overall application stability and SEO.}
      \resumeItemListEnd
   \resumeSubSubheading
    {Associate Software Development Engineer}{Aug. 2024 - Mar. 2025}
    \resumeItemListStart
       \resumeItem{Identified unnecessary cache clearances and proposed a fix during a team huddle. Led the initiative to design and implement a new cache-clearing strategy, reducing cache calls and clearances by 98\%.}
       \resumeItem{Independently identified a bottleneck in the development experience and created a proxy to production data, resolving frontend issues that accounted for 60\% of reported bugs.}
       \resumeItem{Closed a year-old issue by developing chunk prefetching logic, transforming a poor user experience into a smoother, responsive interface.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Development Intern}{Apr. 2022 -- Jun. 2024}
      {YourEngineer}{Mumbai, India}
      \resumeItemListStart
        \resumeItem{Migrated a WordPress application to a modern stack with Node.js, React, and PostgreSQL, deployed it on AWS using infrastructure-as-code, and created custom CI/CD pipelines to streamline deployment and maintenance. This led to a 110\% increase in organic traffic.}
        \resumeItem{Created separate development and production environments, with commit-based hosting for development to enable rapid testing and feedback.}
        \resumeItem{Independently developed a Reddit-style community platform with posts and comments for YourEngineer, supporting 1,000+ monthly users with 99\% uptime.}
        \resumeItem{Proposed and led migration from MongoDB to SQL as the data was highly structured, reducing query latency and improving overall performance.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Ring A Friend} $|$ \emph{Node.Js, PostgreSQL, Kotlin, Jetpack Compose, Android}}{Jan. 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Built a full-stack native Android app with Jetpack Compose (frontend), PostgreSQL (database) and Express REST API (backend), following MVVM best practices.}
            \resumeItem{Implemented real-time sockets, socket and API auth, and Firebase push notifications with a background service worker to trigger emergency alerts (ring even on silent).}
            \resumeItem{Enabled external services or users to ring a device with an accompanying text message (e.g., movie tickets, notifications, bots).}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Kotlin, Python, C/C++, C\#, SQL (Postgres), JavaScript, HTML/CSS} \\
     \textbf{Frameworks}{: React, Node.js, .NET, Jetpack Compose, Angular, Spring Boot} \\
     \textbf{Developer Tools}{: Git, Docker, Amazon Web Services, VS Code, PyCharm, IntelliJ, Shell} \\
     \textbf{Libraries}{: Selenium, Cypress, Axios, Redux, Requests}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
